\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{top=2cm, bottom=2cm, left=3cm, right=2cm}
\usepackage[T2A]{fontenc}
\usepackage[russian]{babel}
\usepackage[hidelinks]{hyperref}
\selectlanguage{russian}


\title{Requirement managment}
\author{Agafonov Vadim}
\date{}
\begin{document}

\maketitle

\section*{1. Questions for Conducting User Interviews}

\subsection*{General Questions:}
\begin{itemize}
    \item What are the main issues with the current credit processing system that you want to address?
    \item Which communication channels with clients are prioritized (chat, SMS, email, social media)?
    \item How is integration with external systems (government agencies, other banks) handled?
    \item Which regulatory requirements (GDPR, AML, Federal Law 152-FZ) must be considered?
    \item What success metrics for the system do you consider key (e.g., application processing speed, fraud reduction)?
\end{itemize}

\subsection*{For Clients:}
\begin{itemize}
    \item What actions should clients perform in their personal account?
    \item Is support for a mobile version or application required?
    \item How do clients prefer to receive notifications (SMS, email, push)?
\end{itemize}

\subsection*{For Employees:}
\begin{itemize}
    \item What tools for assessing creditworthiness are currently in use?
    \item How should the notification system for managers operate?
    \item Are role-based access models needed within teams?
\end{itemize}

\subsection*{Technical Aspects:}
\begin{itemize}
    \item What are the system response time requirements (e.g., application loading ≤2 sec)?
    \item What level of system availability is required (e.g., 99.9\% uptime)?
\end{itemize}

\section*{2. Functional and Non-Functional Requirements}

\subsection*{Functional Requirements (FR):}
\subsubsection*{Module 1: Application Processing}
\begin{itemize}
    \item \textbf{FR1.1}: The client can fill out an online application by providing personal information, the purpose of the credit, and sources of income.
    \item \textbf{FR1.2}: Integration with NBKI for credit history verification via API.
    \item \textbf{FR1.3}: Automatic verification of data completeness (validation of email, TIN, passport).
\end{itemize}

\subsubsection*{Module 2: Scoring}
\begin{itemize}
    \item \textbf{FR2.1}: Calculation of credit scoring based on credit history, income, and demographic data.
    \item \textbf{FR2.2}: Generation of recommendations for the specialist (“Approve”, “Reject”, “Manual Review”).
\end{itemize}

\subsubsection*{Module 3: Document Management}
\begin{itemize}
    \item \textbf{FR3.1}: Uploading documents in PDF, JPEG, PNG formats (max. 10 MB).
    \item \textbf{FR3.2}: Verification of document authenticity via OCR and comparison with registries (FNS).
\end{itemize}

\subsubsection*{Module 4: Communication}
\begin{itemize}
    \item \textbf{FR4.1}: Chat support via Telegram and WhatsApp API.
    \item \textbf{FR4.2}: Automatic notifications regarding the application status (SMS, email, push).
\end{itemize}

\subsection*{Non-Functional Requirements (NFR):}
\begin{itemize}
    \item \textbf{Performance}:
    \begin{itemize}
        \item Application processing in ≤3 minutes under 5000 concurrent sessions.
        \item User account loading in ≤1.5 sec.
    \end{itemize}
    \item \textbf{Security}:
    \begin{itemize}
        \item Data encryption using TLS 1.3.
        \item Two-factor authentication for employees.
    \end{itemize}
    \item \textbf{Scalability}:
    \begin{itemize}
        \item Support for horizontal scaling (Kubernetes).
    \end{itemize}
    \item \textbf{Reliability}:
    \begin{itemize}
        \item Backups every 6 hours.
        \item System recovery in ≤15 minutes after a failure.
    \end{itemize}
    \item \textbf{Compatibility}:
    \begin{itemize}
        \item \textbf{Mobile OS}:
            \begin{itemize}
                \item Android: version 10 and above (with support for WebView 85+).
                \item iOS: version 14 and above.
            \end{itemize}
        \item \textbf{Browsers}:
            \begin{itemize}
                \item Google Chrome: version 90+.
                \item Mozilla Firefox: version 88+.
                \item Safari: version 14+.
                \item Microsoft Edge: version 91+.
            \end{itemize}
        \item \textbf{Screen Resolutions}:
            \begin{itemize}
                \item Support for responsive design for resolutions from 320px (mobile devices) up to 3840px (4K monitors).
            \end{itemize}
        \item \textbf{API}:
            \begin{itemize}
                \item Compatibility with RESTful API (version 2.0).
                \item Support for data formats: JSON, XML.
            \end{itemize}
    \end{itemize}
\end{itemize}

\section*{3. User Stories and Use Cases}

\subsection*{User Stories:}
\begin{itemize}
    \item \textbf{As a client}, I want to sign documents using an electronic signature so that I do not have to visit the bank in person.
    \item \textbf{As an administrator}, I want to configure access rights for new employees to minimize the risk of data breaches.
    \item \textbf{As an analyst}, I want to export data to Excel to build forecasts for the credit portfolio.
    \item \textbf{As a legal advisor}, I want to automatically generate contracts based on approved applications to save time.
    \item \textbf{As an IT specialist}, I want to monitor server load in real time to prevent system failures.
    \item \textbf{As a client}, I want to withdraw an application before it is processed so that I can change the credit terms.
\end{itemize}

\subsection*{Use Case: Updating the Scoring Model}
\begin{itemize}
    \item \textbf{Actors}: Analytics Department, System.
    \item \textbf{Steps}:
    \begin{enumerate}
        \item Analysts upload a new version of the ML model.
        \item The system performs A/B testing on 10\% of the applications.
        \item If the test is successful (accuracy >90\%), the model is deployed for all applications.
        \item The old model is retained as a backup for 30 days.
    \end{enumerate}
\end{itemize}

\subsection*{Use Case: Processing a GDPR Request}
\begin{itemize}
    \item \textbf{Actors}: Client, System, Administrator.
    \item \textbf{Steps}:
    \begin{enumerate}
        \item The client submits a data deletion request through their personal account.
        \item The system verifies that there are no active credits.
        \item Data is anonymized within 72 hours.
        \item The administrator confirms the completion of the request.
    \end{enumerate}
\end{itemize}

\subsection*{Use Case: Integration with GIS GMP}
\begin{itemize}
    \item \textbf{Actors}: System, GIS GMP (state system).
    \item \textbf{Steps}:
    \begin{enumerate}
        \item Upon credit approval, the system generates an electronic receipt.
        \item The data is automatically sent to GIS GMP via API.
        \item The system checks the payment processing status every 15 minutes.
        \item In case of an integration error, a manual verification process is initiated.
    \end{enumerate}
\end{itemize}

\section*{4. Error Handling Scenarios}

\subsection*{Scenario 1: NBKI Integration Error}
\begin{itemize}
    \item \textbf{Condition}: API is unavailable for more than 30 seconds.
    \item \textbf{Actions}:
    \begin{enumerate}
        \item Save the application with the status “Pending”.
        \item Notify technical support.
        \item Retry the request after 5 minutes (up to 3 attempts).
        \item If all attempts are exhausted, notify the client: “The verification is taking longer than expected.”
    \end{enumerate}
\end{itemize}

\subsection*{Scenario 2: Invalid Document}
\begin{itemize}
    \item \textbf{Condition}: An unreadable file has been uploaded.
    \item \textbf{Actions}:
    \begin{enumerate}
        \item Reject the document.
        \item Send a message to the client requesting to re-upload the file.
    \end{enumerate}
\end{itemize}

\section*{5. Regulatory Requirements}

\begin{itemize}
    \item \textbf{GDPR}:
    \begin{itemize}
        \item Explicit client consent for data processing.
        \item Data deletion upon request within 72 hours.
    \end{itemize}
    \item \textbf{AML/KYC}:
    \begin{itemize}
        \item Client verification against sanctions lists (OFAC, EU).
        \item Audit log of employee actions.
    \end{itemize}
    \item \textbf{Federal Law 152-FZ (RF)}:
    \begin{itemize}
        \item Data storage on servers located within the Russian Federation.
        \item Encryption when transmitting data outside the bank.
    \end{itemize}
    \item \textbf{PCI DSS}:
    \begin{itemize}
        \item Prohibition on storing CVV/CVC codes.
        \item Annual security audit.
    \end{itemize}
\end{itemize}

\section*{6. Analysis of Requirements Completeness}

\subsection*{Strengths:}
\begin{itemize}
    \item Key roles (clients, employees, administrators) have been considered.
    \item Detailed modules (scoring, documents, communication).
    \item Regulatory requirements (GDPR, Federal Law 152-FZ) are covered.
\end{itemize}

\subsection*{Weaknesses:}
\begin{itemize}
    \item No requirements for auditing changes to applications.
    \item Data recovery scenarios in case of hardware failures are not described.
\end{itemize}

\subsection*{Recommendations:}
\begin{itemize}
    \item Add an audit log to track employee actions.
    \item Clarify integration with messaging apps (e.g., via WhatsApp Business API).
    \item Include an SLA for external APIs (maximum response time — 2 sec).
\end{itemize}

\section*{Final Document}

\subsection*{Application Value:}
\begin{itemize}
    \item Accelerating application processing by 40\% through automation.
    \item Reducing fraud risks via integration with AML services.
    \item Ensuring compliance with GDPR and Federal Law 152-FZ for operations in the Russian Federation and the EU.
\end{itemize}

\end{document}
