\documentclass[20pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[english]{babel}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{arcs}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{stackrel}
\usepackage{xcolor}
\usepackage[fontsize=12pt]{fontsize}
\pagestyle{plain}

\begin{document}
\pagestyle{empty}
\normalsize

\title{Laboratory Work No. 1 \\
Topic Selection and Requirements Formation}
\author{Agafonov Vadim M3310 367787}
\date{}
\maketitle

\centerline{\LARGE\textbf{"Bank Credit Department System"}}

\section{System Description}

\textbf{"Bank Credit Department System"} is designed for optimizing the processing and analysis of credit-related processes within the bank. The main features of the system include:

\begin{itemize}
    \item \textbf{Credit Application Processing}: Creation, submission, and processing of credit applications.
    \item \textbf{Scoring and Creditworthiness Assessment}: Automated analysis of the creditworthiness of the applicant.
    \item \textbf{Document Management}: Creation, modification, storage, and transmission of documents.
    \item \textbf{Customer Communication}: Communication with customers through all available channels (chat, SMS, messengers, social networks, etc.).
    \item \textbf{Reporting and Analytics}: Creation of reports for evaluating the credit portfolio and monitoring its status.
    \item \textbf{Integration with External Systems}: Interaction with other credit organizations, government agencies, etc.
\end{itemize}

\section{Key Actors}

\begin{itemize}
    \item \textbf{Customers}: Individuals and legal entities submitting credit applications.
    \item \textbf{Credit Specialists}: Employees responsible for processing and analyzing credit applications.
    \item \textbf{Customer Relationship Managers}: Employees who communicate with customers, guiding them from start to finish.
    \item \textbf{Analysts}: Specialists providing information about the productivity of the department and responsible for reporting.
    \item \textbf{System Administrators}: Technical specialists maintaining system functionality and improving its fault tolerance.
    \item \textbf{Department Managers}: Managers responsible for risk management and making strategic decisions.
    \item \textbf{Lawyers}: Specialists dealing with legal aspects of all agreements and documents.
    \item \textbf{Financial Analysts}: Employees analyzing and forecasting the economic situation and preparing reports.
    \item \textbf{Security Specialists}: Specialists responsible for system security, data preservation, fraud prevention, and cyber attacks.
\end{itemize}

\section{Actions, Access, and Capabilities for Key Actors}

\subsection{Customers}
\begin{itemize}
    \item \textbf{Actions}: Creating, modifying, and submitting applications, providing documents.
    \item \textbf{Access}: User's personal account.
    \item \textbf{Capabilities}: Monitoring application status, communicating with specialists through communication channels (chat or email).
\end{itemize}

\subsection{Credit Specialists}
\begin{itemize}
    \item \textbf{Actions}: Processing applications, making credit decisions.
    \item \textbf{Access}: Application management system, client documents, scoring system.
    \item \textbf{Capabilities}: Viewing, editing applications, generating reports and providing them to management.
\end{itemize}

\subsection{Customer Relationship Managers}
\begin{itemize}
    \item \textbf{Actions}: Communicating with customers, consulting on credit products.
    \item \textbf{Access}: Client documents, chat, corporate email.
    \item \textbf{Capabilities}: Creating applications, editing applications, requesting and providing documents.
\end{itemize}

\subsection{Analysts}
\begin{itemize}
    \item \textbf{Actions}: Data analysis, portfolio monitoring, report preparation.
    \item \textbf{Access}: General data on the work of the credit department, analysis tools.
    \item \textbf{Capabilities}: Creating, editing, and providing reports.
\end{itemize}

\subsection{System Administrators}
\begin{itemize}
    \item \textbf{Actions}: System maintenance, corporate computer setup, server setup and maintenance, problem resolution, error control.
    \item \textbf{Access}: Full access to the system and its settings.
    \item \textbf{Capabilities}: System configuration, user access management, data security.
\end{itemize}

\subsection{Department Managers}
\begin{itemize}
    \item \textbf{Actions}: Monitoring employee performance, making strategic decisions.
    \item \textbf{Access}: Reports, tasks, chat, email.
    \item \textbf{Capabilities}: Viewing reports, managing personnel through communication channels (chat, email).
\end{itemize}

\subsection{Lawyers}
\begin{itemize}
    \item \textbf{Actions}: Creating, checking, and preparing legal documents, consulting on legal issues.
    \item \textbf{Access}: Document database.
    \item \textbf{Capabilities}: Viewing, creating, and editing documents.
\end{itemize}

\subsection{Financial Analysts}
\begin{itemize}
    \item \textbf{Actions}: Analyzing and forecasting the economic situation, preparing reports.
    \item \textbf{Access}: Access to data related to the financial component of the department.
    \item \textbf{Capabilities}: Creating, editing, and providing reports.
\end{itemize}

\subsection{Security Specialists}
\begin{itemize}
    \item \textbf{Actions}: Ensuring protection against all types of attacks, fraud, system monitoring.
    \item \textbf{Access}: Full access to the security system and data.
    \item \textbf{Capabilities}: Preventing attacks, changing user access rights, data control.
\end{itemize}

\section{Application Value Description}

\begin{itemize}
    \item \textbf{Accelerate application processing}: Automation of the system helps specialists analyze the application faster and make a decision.
    \item \textbf{Improve creditworthiness assessment accuracy}: Increasing the security of the bank's credit department from dishonest individuals, whose actions lead to financial losses.
    \item \textbf{Enhance customer communication}: Supporting customers at all stages allows for improving service and customer trust.
    \item \textbf{Ensure transparency and control}: Impossibility of falsification and fraud from the side of company employees, thanks to control over the application at all stages by different specialists.
    \item \textbf{Enhance data security}: Integration with external systems allows for increasing data security and protecting confidential information.
    \item \textbf{Optimize personnel management}: The ability to control personnel and instant communication with them allows for increasing the efficiency of the department.
\end{itemize}

\bibliographystyle{alpha}

\end{document}
